Open Preprints in Ecology \& Evolution

### 2012-09-10 ms.tex
Reviewed and edited; added a bit to conclusion
I reviewed and edited for minor grammar and corrected a few things of the
existing text.  I also added more to the conclusion paragraph, but This
paragraph still needs a little more.

Preprints servers such as arXiv are common in mathematics and physics, but
still a minority of papers in ecology and evolution use them. Preprints
servers allow author to make their manuscripts publicly available before, or
in parallel to, submitting them to journals for traditional peer-review. ...
The idea became popular with arXiv, and many physicists start their day with a
look at the new papers in arXiv \cite{gin11}

@@

The review process as a whole is critically over-loaded, because the number of
active scientists increases, because the pressure to publish increases, and
because of an effect dubbed ``the tragedy of the reviewers commons'' REF.  In
the same times, rejection rates are high in most journals (REF), and when the
not invited to submit a revisions, authors are left with the impression that
they must start the whole process all over again. It's thus no surprize that
different initiatives emerged over the last few years, to decrease the time
spent in review. XXX et coll. (REF) called for the recycling and reuse of
peer-reviews: by attaching previous reviews, and detailed replies, to a new
submission, both the editor and the referees can jauge the work done on the
manuscript, and perhaps evaluate it with less prejudice. In a similar way, the
\emph{Peerage of Science} initiative allows authors to seek anonymous pre-
review by their peers. Some journals (LIST?) now accept to publish papers
which received good evaluations, effectively outsourcing the review process. A
widespread use of preprint servers can achieve the same goal of reducing the
time spent in review. By putting a manuscript out there for open comments and
criticisms, the authors will receive valuable feedback, and can improve the
version which will be submitted. With a rich enough community of scientists
depositing preprints, and commenting on them, the process of an open pre-
review can become widespread, and will overall increase the quality of first
submissions.
% Assuming that the quality of the paper is a good prior of its acceptance probability :-)

@@

Preprint servers also establish priority in a fair way. Some manuscript will
spend much more time in the review process. Public preprints server offer a
much fairer way to establish intellectual priority by making the work
available when done, and even if the exact organisation of the manuscript may
change. Surprisingly, there is perception in biology that public preprints
make it easier to steal ideas, as if scientific ideas only took form in
published material.
% TP This needs more development, I'm not sure I get your point
Mathematicians and physicists have embraced arXiv in part
to establish priority in a fair way\cite{cal12}.

Some of the responses to public preprints are surprising since they are,
essentially, the same as exchanging preprints among colleagues.
% TP Well, no. You trust your colleagues, and you trust that they will not give your
%    MS to anyone!
Prepublication reviews by a small network of colleagues is an important part
of the scientific process, which is attested by the fact that nearly all
published papers acknowledge comments by people not listed as co-authors.
Preprints servers simply offer a way to extend this network of colleagues to
the entire scientific community. It ensures that science is not constrained by
small networks of scientists exchanging ideas. Ginsparg made arXiv.org in part
for democratic reasons: he wanted everyone from graduate students in small
universities to Princeton professors to have access to the most recent
scientific \emph{ideas}.
% TP One important point to make: the MS and the idea are different things.
%    We should focus more on the later...
Ginsparg revolutionary idea was simply to use the power of the internet for
preprints, not just for the end product, so the process can be open from A to
Z, instead of being just open at the end of the process.
% TP Since when is the publishing buisness an open process? :-)

@@

Responding to the rumour that they refused manuscripts submitted to arXiv,
Nature responded that ``Nature never wishes to stand in the way of communication
between researchers. We seek rather to add value for authors and the community
at large in our peer review, selection and editing'' \cite{nat05}.

>>>>

Preprint servers such as arXiv are common in mathematics and physics,
but still a minority of papers in ecology and evolution use
them. Preprint servers allow authors to make their manuscripts
publicly available before, or at the same time as, submitting them to
journals for traditional peer-review. ...  The idea became popular
with arXiv, and many physicists start their day with a look at the new
papers in ArXiv \cite{gin11}

@@

The review process as a whole is critically over-loaded, because the
number of active scientists increases, because the pressure to publish
increases, and because of an effect dubbed ``the tragedy of the
reviewers commons'' REF.  At the same time, rejection rates are high
in most journals (REF), and when not invited to submit revisions,
authors are left with the impression that they must start the whole
process all over again. It's thus no surprise that different
initiatives emerged over the last few years to decrease the time spent
in review. XXX et coll. (REF) called for the recycling and reuse of
peer-reviews: by attaching previous reviews, and detailed replies, to
a new submission, both the editor and the referees can gauge the work
done on the manuscript, and perhaps evaluate it with less
prejudice. In a similar way, the \emph{Peerage of Science} initiative
allows authors to seek anonymous pre- review by their peers. Some
journals (LIST?) now accept papers for publication that received good
evaluations, effectively outsourcing the review process. A widespread
use of preprint servers can achieve the same goal of reducing the time
spent in review. By putting a manuscript out there for open comments
and criticisms, the authors will receive valuable feedback, and can
improve the version which will be submitted. With a rich enough
community of scientists depositing preprints, and commenting on them,
the process of an open pre- review can become widespread, and will
overall increase the quality of first submissions.
% Assuming that the quality of the paper is a good prior of its acceptance probability :-)

@@

Preprint servers also establish priority in a fair way.  Some
manuscripts will spend much more time in the review process than
others.  Public preprint servers offer a much fairer way to establish
intellectual priority by making the work available when done, even if
the exact organisation of the manuscript may change. Surprisingly,
there is a perception in biology that public preprints make it easier
to steal ideas, as if scientific ideas only took form in published
material.
% TP This needs more development, I'm not sure I get your point
Mathematicians and physicists have embraced arXiv in part to establish
priority in a fair way\cite{cal12}.

Some of the responses to public preprints are surprising since they are,
essentially, the same as exchanging preprints among colleagues.
% TP Well, no. You trust your colleagues, and you trust that they will
% not give your MS to anyone!
Prepublication reviews by a small network of colleagues is an
important part of the scientific process, which is attested by the
fact that nearly all published papers acknowledge comments by people
not listed as co-authors.  Preprint servers simply offer a way to
extend this network of colleagues to the entire scientific
community. It ensures that science is not constrained by small
networks of scientists exchanging ideas.  Paul Ginsparg created
arXiv.org in part for democratic reasons: he wanted everyone from
students in small universities to Ivy-League professors to have access
to the most recent scientific \emph{ideas}.
% TP One important point to make: the MS and the idea are different things.
%    We should focus more on the later...
Ginsparg's revolutionary idea was simply to use the power of the
internet for preprints, not just for the end product, so the process
can be open from A to Z, instead of being just open at the end of the
process.
% TP Since when is the publishing buisness an open process? :-)

@@

Responding to the rumour that they refused manuscripts submitted to arXiv,
Nature responded that ``Nature never wishes to stand in the way of communication
between researchers. We seek rather to add value for authors and the community
at large in our peer review, selection and editing'' \cite{nat05}.
Posting preprints online increases the community of available informal
peer reviewers, and uses the internet for its original
community-building purposes.  Preprint servers also facilitate
communication between disciplines, bridging cultural as well as
geographic divides.
% JA: perhaps something less advertising-like should go here:
The advantages are clear and the costs are low.
% BUY NOW!
